Reproducible Research/ Peer Assessment 1
========================================================


## 1.Loading and preprocessing the data


```{r}
setwd("../Downloads")
data<-read.csv("./activity.csv",sep=",")
data$date<-as.Date(data$date,"%Y-%m-%d")

```

## 2.What is mean total number of steps taken per day?


```{r}
install.packages("reshape2")
library(reshape2)
datamelt<-melt(data,id=c("date"),measure.vars=c("steps"),na.rm=TRUE)
data_sum<-dcast(datamelt,date~variable,sum)

```

Now with our new data frame we can create our histogram of the total number of steps taken each day:

```{r fig.width=7, fig.height=6}
hist(data_sum$steps,col="blue",xlab="")
```

The mean and the median total number of steps taken per day are calculated as below:
```{r}
mean(data_sum$steps)
```

```{r}
median(data_sum$steps)
```

## 3.What is the average daily activity pattern?



```{r}
datamelt2<-melt(data,id=c("interval"),measure.vars=c("steps"),na.rm=TRUE)
interval<-dcast(datamelt2,interval~variable,mean)
head(interval)
```

```{r fig.width=7, fig.height=6}
plot(interval$interval, interval$steps,type="l",xlab="Intervals",ylab="Average",col="red",lwd=2)
```


```{r}
interval[interval$steps==max(interval$steps),1]
(interval[interval$steps==max(interval$steps),1])/5
```


## 4.Imputing missing values

```{r}
data1 <-subset(data, !is.na(steps))
nrow(data)
nrow(data1)
missing<-nrow(data)-nrow(data1)
No_of_missing

```


```{r}
newData<-data
for (i in 1:nrow(newData)){
  if (is.na(newData[i,1])){
    newData[i,1]<-interval[(interval[,1]==newData[i,3]),2]
  }
}
head(newData)

```
Now we use the same method to creat the histogram for the new data set where the NA values were replaced :
```{r}
new_datamelt<-melt(newData,id=c("date"),measure.vars=c("steps"),na.rm=TRUE)
new_data_sum<-dcast(new_datamelt,date~variable,sum)

```

```{r fig.width=7, fig.height=6}
hist(new_data_sum$steps,col="green")
```

```{r}
mean(new_data_sum$steps)
median(new_data_sum$steps)
```

If we compare the new values with those from section 2:
```{r echo=FALSE}
mean(data_sum$steps)
median(data_sum$steps)
```

## 5.Are there differences in activity patterns between weekdays and weekends?

```{r}
factorData<-data
factorData$date<-weekdays(factorData$date)

```
```{r}
for (i in 1:nrow(factorData)){
  if (factorData[i,2]=="일요일" | factorData[i,2]=="토요일"){
    factorData[i,2]<-"weekend"
  } else {
    factorData[i,2]<-"weekdays"
  }
}
head(factorData)
```
```{r fig.width=11, fig.height=6 }
library(lattice)
plot<-xyplot(factorData$steps~ factorData$interval | factorData$date, data=factorData, layout = c(1, 2),type="l",xlab="Interval",ylab="Number")
print(plot)
```
