Reproducible Research Peer Assessment1

==============================================


1.Loading and preprocessing the data

```{r}

activity = read.csv("activity.csv")  ## Load the Data
activity$date = as.Date(data$date,"%Y-%m-%d") ##Transform/Process the data in to a format suitable for analysis
activity = as.data.frame(activity)
```

2. What is mean total number of steps taken per day?

Use "reshape2" pacakges to caluclate total numbers.

```{r}
library(reshape2)
library(ggplot2)


activitymeltdate = melt(activity,id=c("date"),measure.vars=c("steps"),na.rm=TRUE) ##Ignor the missing value in the Dataset.
activitysum = dcast(activitymeltdate, date ~ variable, sum)
```

```{r = fig.width = 7, fig.height = 5}
hist(activitysum$steps, col = "blue") #make a histogram of the totalnumber of steps taken each day.

qplot(x = steps, data = activitysum)

## another way.

mean(activity$steps) 

median(activity$steps)
```

3. What is the average daily activity pattern?



```{r}
activitymeltinterval = melt(activity, id = c("interval"),measure.vars = c("steps"), na.rm = TRUE)
                     <-melt(data,id=c("interval"),measure.vars=c("steps"),na.rm=TRUE)
activitymean = dcast(activitymeltinterval, interval ~ variable, mean)
```

```{r = fig.width = 7, fig.height = 5}
plot(activitymean$interval, activitymean$steps, type = "l", xlab = "Interval", ylab = "Average of Steps" )

interval[activitymean$steps==max(activitymean$steps),1] ## contain max number of steps


```


4. Imputing missing values.

Calculate and report the total number of missing values in the dataset

```{r}
missing = subset(activity, !is.na(steps))

NAmissing = nrow(activity) - nrow(missing)  
NAmissing ## number of missing Values. 
```

replace the NA values to replace them with the average of steps all days for each interval. 
```{r}
activity2 = activity
for (i in 1:nrow(activity2)){
  if (is.na(activity2[i,1])){
    activity2[i,1]<-interval[(activitymean[,1]==activity2[i,3]),2]
  }
}
```

reproduce data to make Histogram
```{r}
activitymeltdata2 = melt(activity2,id=c("date"),measure.vars=c("steps"),na.rm=TRUE)

activitysum2 = dcast(activitymeltdata2,date~variable,sum)

hist(activitysum2$steps,col="green",xlab="") #Makes the histogram relace NA values.

mean(activitysum2$steps) # mean of the steps of which replace NA values.  

median(activitysum2$steps) # median 

```

5. Are there differences in activity patterns between weekdays and weekends?

```{r}

activityFactor = activity
activityFactor$date = weekdays(activityFactor$date)


for (i in 1:nrow(activityFactor)){
  if (activityFactor[i,2]=="Sunday" | activityFactor[i,2]=="Saturday"){
    activityFactor[i,2]="weekend"
  } else {
    activityFactor[i,2]="weekdays"
  }
}



library(lattice)
xyplot(activityFactor$steps~ activityFactor$interval |activityFactor$date, data=activityFactor, layout = c(1, 2),type="l")


```
